% Formatting
\documentclass[10pt, oneside, a5paper]{article}

%% Fixers
\usepackage{fontspec}
\usepackage{realscripts}
\usepackage{xunicode}
\usepackage{polyglossia}

\usepackage[]{microtype}
\usepackage[]{geometry}
\geometry{a5paper}
%% \usepackage[]{geometry}
\usepackage[english]{isodate}

% Packages
\usepackage{lastpage}
%% \usepackage{scrlayer-scrpage}
\usepackage{enumitem}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{newunicodechar}

%Load Last Fixers
\usepackage{hyperref}

% Settings

\setdefaultlanguage{english}
\setotherlanguage{latin}

\setmainfont{Latin Modern Roman}[Ligatures=TeX,Fractions=On]
\setsansfont{Latin Modern Sans}[Ligatures=TeX,Fractions=On]
\setmonofont{Latin Modern Mono}[Ligatures=TeX,Fractions=On]

\hypersetup{bookmarksopen=true,colorlinks=true,allcolors=blue}

\linespread{1.00625}
\showboxdepth=\maxdimen
\showboxbreadth=\maxdimen

\setlist{left=\parindent, itemsep=0.03em}

%% \KOMAoption{parskip}{no}
%% \setlength{\parindent}{0pt}

\setcounter{secnumdepth}{0}

\pagestyle{empty}

% Symbol
\usepackage{tikz}
\usetikzlibrary{svg.path}

% SVG path from Sarang:
% https://upload.wikimedia.org/wikipedia/commons/a/ac/U%2B262D.svg
\newcommand*{\hamsic}{%
  \begingroup
    \settoheight{\dimen0 }{H}%
    \resizebox{!}{\dimen0 }{%
      \tikz\fill svg[yscale=-1]{%
        M67,80l13,19L130,65L108,52z%
        M54,103A60,60 0 1,0 55,23A50,50 0 1,1 55,101z%
        m0,0L14,160l19,10L64,110z%
        M95,87l46,79l17,-12L108,79z%
      };%
    }%
  \endgroup
}

\newcommand*{\httpref}[1]{\href{https://#1}{\nolinkurl{#1}}}
  
\newunicodechar{☭}{\hamsic}

\setlist{label=☭}

\author{}
\date{}

\begin{document}

{%
  \raggedright{}
  {\bfseries{}\LARGE{}Evil Billionaires}\\
  Pandemic! Conspiracy! Martians?%
}

\bigskip{}

The great recession, COVID-19, housing and now Donald Trump. What is
going on?

\section*{Empire is Falling}

For a brief movement after World War II, a few ``normals'' in the
imperial core could make it. These privileges came at the expense of
billions.

We were the house slaves of Statesian empire, and the periphery
nations were the field slaves. All systems built on oppression fall
apart. The system decays, and the oppressed rebel.

Civil rights, Vietnam, Afghanistan, Gaza. On so many fronts, the
empire lost and is losing.

\section*{They Won't Save Us}

Do we house slaves join the field slaves in their struggle, or do we
fall with our masters?  The fascists have chosen their side, have you
chosen yours?

It's time to stop voting {NDP}, and it's time to start organizing
outside the capitalist state.  We need real change, and the servants
of empire won't give us that.

\section*{Workers Unite}

We workers must solve the issues the capitalists and their servants
can't. The fascists are coming, and there is no time left to
dawdle. Organize. Agitate. Fight.

 %% Capitalism is war, division and theft. Socialism can
%% bring us peace, reparations and liberty; but we must work for it. 

\end{document}
